Fourmile Calibrations and Output

### 2023-05-05 38HRU_model/fourmile_model_outputs.Rmd
flow added, burn params edited

```{r}
params <- params %>%
  mutate(burn = 'no')

params_combo <- bind_rows(params,
                          burn_params %>%
                            rename(param = params))

@@

name <- levels(params_combo$param)

>>>>

```{r}
params2 <- params %>%
  mutate(burn = 'no') %>%
  filter(param %in% c('a_rain',
                        'a_snow',
                        'soilMaxInfSummer',
                        'soilMaxDPS',
                        'lagSurfaceRunoff',
                        'soilDistMPSLPS'))

params_combo <- bind_rows(params2,
                          burn_params %>%
                            rename(param = params))

@@

#name <- levels(params_combo$param)

lapply(name2, plot_params)
